---
title: "Importing and Transforming Data Exercises"
author: Ai Yukino
output: pdf_document
urlcolor: blue
---

## Import packages

```{r}
library(tidyverse)
library(readxl)
library(AER)
```

## Exercise 1

### List all example files available with the readr library.

```{r}
readr_example()
```

\newpage

## Exercise 2

### Read the `mtcars.csv` file.

```{r message = FALSE}
file_path <- readr_example("mtcars.csv")
read_csv(file = file_path)
```

\newpage

## Exercise 3

### Read the first 10 lines from the `mtcars.csv` file.

```{r message = FALSE}
file_path <- readr_example("mtcars.csv")
read_csv(file_path, n_max = 10)
```

\newpage

## Exercise 4

### Read the `example.log` file.

```{r message = FALSE}
file_path <- readr_example("example.log")
read_csv(file_path)
```

\newpage

## Exercise 5

### List all sheets in `readxl_example("datasets.xlsx")`.


```{r}
file_path <- readxl_example("datasets.xlsx")
excel_sheets(file_path)
```

\newpage

## Exercise 6

### Read data from the last sheet.

```{r}
file_path <- readxl_example("datasets.xlsx")
read_xlsx(file_path, sheet = "quakes")
```

\newpage

## Exercise 7

### Load the `dplyr` package. Install and load the `AER` package and run the command `data("Fertility")` which loads the dataset Fertility to your workspace. Take a `glimpse()` at the data.

```{r}
data("Fertility")
glimpse(Fertility)
```

\newpage

## Exercise 8

### Select rows 35 to 50 and print to console its age and work entry.

```{r}
Fertility %>%
  {.[c(35, 50),]} %>%
  select(age, work)
```

\newpage

## Exercise 9

### Select the last row in the dataset and print to console.

```{r}
tail(Fertility, 1)
```

\newpage

## Exercise 10

### Count how many women proceeded to have a third child.

```{r}
Fertility %>%
  filter(morekids == "yes") %>%
  nrow()
```

\newpage

## Exercise 11

### There are four possible gender combinations for the first two children. Which is the most common?

```{r}
ff <- Fertility %>%
  filter(gender1 == "female", gender2 == "female") %>%
  nrow()
fm <- Fertility %>%
  filter(gender1 == "female", gender2 == "male") %>%
  nrow()
mm <- Fertility %>%
  filter(gender1 == "male", gender2 == "male") %>%
  nrow()
mf <- Fertility %>%
  filter(gender1 == "male", gender2 == "female") %>%
  nrow()

tb <- tibble(gender_pair = c("female-female", "female-male",
                       "male-male", "male-female"),
       count = c(ff, fm, mm, mf))
tb
```

So the "male-male" pair is most common.
