---
title: "Model Exercises"
author: Ai Yukino
output: pdf_document
urlcolor: blue
---

[HW link](https://titus.techtalentsouth.com/mod/assign/view.php?id=56556)

## Import packages

```{r}
library(tidyverse)
library(modelr)
```

\newpage

## Exercise 1

Familiarize yourself with the `heights` data set provided with the `modelr` package.

### Solution

```{r}
data(heights)
heights
# ?heights
```

\newpage

## Exercise 2

Create a list of formulas for modeling income with:

- `height`
- `height` $\cdot$ `weight`
- linear combination of all variables

### Solution

```{r}
concat_col <- paste(colnames(heights)[-1], collapse=" + ")

formulas <- paste0("income ~ ", c("height", "height * weight", concat_col))

formulas
```

\newpage

## Exercise 3

From the data, remove rows containing NA’s. Fit the linear model with the formulas from exercise 2.

### Solution

```{r}
heights <- heights %>%
  drop_na()
```

```{r}
model_height <- lm(formula = formulas[1], data = heights)
model_height_times_weight <- lm(formula = formulas[2], data = heights)
model_all <- lm(formula = formulas[3], data = heights)
```


```{r}
summary(model_height)
```

```{r}
summary(model_height_times_weight)
```

```{r}
summary(model_all)
```

\newpage

## Exercise 4

For each fit, calculate RMSE.

### Solution

```{r}
rmse(model_height, heights)
```

```{r}
rmse(model_height_times_weight, heights)
```

```{r}
rmse(model_all, heights)
```

\newpage

## Exercise 5

For each model, add residuals to the data and plot their distribution. (Hint: use `lift_dl()`.)

### Solution

```{r}
residuals <- resid(model_height)

ggplot(data = heights, aes(x = income, y = residuals)) + 
  geom_point()
```

\newpage

```{r}
residuals <- resid(model_height_times_weight)

ggplot(data = heights, aes(x = income, y = residuals)) + 
  geom_point()
```

\newpage

```{r}
residuals <- resid(model_all)

ggplot(data = heights, aes(x = income, y = residuals)) + 
  geom_point()
```